%%% Seznam použité literatury je zpracován podle platných standardů. Povinnou citační
%%% normou pro bakalářskou práci je ISO 690. Jména časopisů lze uvádět zkráceně, ale jen
%%% v kodifikované podobě. Všechny použité zdroje a prameny musí být řádně citovány.

\def\bibname{Bibliography}
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\bibname}


\bibitem{khanova_skola}
O Khanově škole. \emph{Khanova škola} [online]. [cit. 2015-07-16]. Available from: https://www.khanovaskola.cz/o-skole


%\bibitem{lamport94}
%  {\sc Lamport,} Leslie.
%  \emph{\LaTeX: A Document Preparation System}.
%  2. vydání.
%  Massachusetts: Addison Wesley, 1994.
%  ISBN 0-201-52983-1.

\bibitem{1}
{\sc Bower,} Beverly L. {\sc Hardy,} Kimberly P.
From correspondence to cyberspace: Changes and challenges in distance education.
\emph{New Directions for Community Colleges} [online], 2004, 2004(128): 5-12 . DOI: 10.1002/cc.169.
\bibitem{2}
Last Week Tonight with John Oliver: Student Debt (HBO). \emph{YouTube} [online]. 7.9.2014, [cit. 2015-07-09]. Available from: https://www.youtube.com/watch?v=P8pjd1QEA0c
\bibitem{3}
Online, All Students Sit in the Front Row. GATES, Bill. \emph{gatesnotes} [online]. November 18, 2014, [cit. 2015-12-03]. Available from: http://www.gatesnotes.com/Education/Colleges-Without-Walls-Arizona
\bibitem{4}
In the Developing World, MOOCs Start to Get Real. LEBER Jessica. \emph{MIT Technology Review} [online]. March 15, 2013, [cit. 2015-07-16]. Available from: http://www.technologyreview.com/news/512256/in-the-developing-world-moocs-start-to-get-real/

\bibitem{5}
\emph{Kepler kigali} [online]. © 2015, [cit. 2015-07-16]. Available from: http://kepler.org

\bibitem{6}
\emph{Generation Rwanda} [online]. [cit. 2015-07-16]. Available from: http://www.generationrwanda.org

\bibitem{moodle}
\emph{Moodle} [online]. [cit. 2015-07-16]. Available from: https://moodle.org

\bibitem{moodle_usage}
Moodle Statistics. \emph{moodle.net} [online]. 2015, [cit. 2015-07-16]. Available from: https://moodle.net/stats


\bibitem{9}
\emph{Coursera} [online]. © 2015, [cit. 2015-03-03]. Available from: https://www.coursera.org/about
\bibitem{10}
\emph{YouTube.com} [online]. © 2015, [cit. 2015-07-16]. Available from: https://www.youtube.com
\bibitem{11}
The top 500 sites on the web. \emph{Alexa} [online]. 2015, [cit. 2015-07-16]. http://www.alexa.com/topsites

\bibitem{numberphile_youtube}
\emph{Numberphile Youtube channel} [online]. © 2015, [cit. 2015-07-16]. Available from: https://www.youtube.com/user/numberphile
\bibitem{veritasium_youtube}
\emph{Veritasium YouTube channel} [online]. © 2015, [cit. 2015-07-16]. Available from: https://www.youtube.com/user/veritasium
\bibitem{khan_academy_youtube}
\emph{Khan Academy YouTube channel} [online]. © 2015, [cit. 2015-07-16]. Available from: https://www.youtube.com/user/khanacademy


\bibitem{educreations}
\emph{Educreations} [online]. © 2015, [cit. 2015-07-15]. Available from: https://www.educreations.com

\bibitem{showme}
\emph{ShowMe} [online]. © 2015, [cit. 2015-07-15]. Available from: https://www.showme.com


\bibitem{khan_academy}
\emph{Khan Academy} [online]. © 2015, [cit. 2015-07-08]. Available from: https://www.khanacademy.com

\bibitem{khanova_skola}
\emph{Khanova škola} [online]. [cit. 2015-07-16]. Available from: https://khanovaskola.cz



\bibitem{content_range}
Hypertext Transfer Protocol (HTTP/1.1): Range Requests [online]. June 2014, [cit. 2015-07-16]. Available from: https://tools.ietf.org/html/rfc7233

% 05_Choice of technologies

\bibitem{java}
Java applet. \emph{Wikipedia, the free encyclopedia} [online]. Last modified on 4 July 2015, [cit. 2015-07-08]. Available from: https://en.wikipedia.org/wiki/Java\_applet

\bibitem{java_mobile}
How do I get Java for Mobile device?. \emph{Java.com} [online]. [cit. 2015-04-16]. Available from: http://www.java.com/en/download/faq/java\_mobile.xml

\bibitem{flash}
Adobe Flash Player/Features. \emph{Adobe.com} [online]. © 2015, [cit. 2015-07-08]. Available from: http://www.adobe.com/cz/products/flashplayer/features.html

\bibitem{steve_jobs}
Thoughts on Flash. JOBS Steve. \emph{Apple.com} [online]. April 2010, [cit. 2015-04-16]. Available from: http://www.apple.com/hotnews/thoughts-on-flash

\bibitem{adobe_mobile}
An Update on Flash Player and Android. ALJABER Tareq. \emph{Adobe AIR and Adobe Flash Player Team Blog} [online]. June 28, 2012, [cit. 2015-04-16]. Available from: http://blogs.adobe.com/flashplayer/2012/06/flash-player-and-android-update.html

\bibitem{swf_doc}
SWF and AMF Technology Center. \emph{Adobe.com} [online]. © 2015, [cit. 2015-07-08]. Available from: http://www.adobe.com/devnet/swf.html

\bibitem{mobile_statistics}
Mobile Marketing Statistics 2015. BOSOMWORTH Danyl. \emph{Smart Insights} [online]. January 15, 2015, [cit. 2015-04-16]. Available from: http://www.smartinsights.com/mobile-marketing/mobile-marketing-analytics/mobile-marketing-statistics

\bibitem{silverlight}
Get Silverlight 5. \emph{Microsoft Silverlight} [online]. [2015-04-16]. Available from: http://www.microsoft.com/silverlight/

\bibitem{silverlight_is_dead}
Moving to HTML5 Premium Media. \emph{Microsoft Edge Dev Blog} [online]. July 2, 2015, [cit. 2015-07-08]. Available from: http://blogs.windows.com/msedgedev/2015/07/02/moving-to-html5-premium-media

\bibitem{edge_getusermedia}
Announcing media capture functionality in Microsoft Edge. \emph{Microsoft Edge Dev Blog} [online]. May 13, 2015, [cit. 2015-07-16]. Available from: http://blogs.windows.com/msedgedev/2015/05/13/announcing-media-capture-functionality-in-microsoft-edge

\bibitem{javascript_vs_ecmascript}
A brief history of ECMAScript versions (including Harmony/ES.next). RAUSCHMAYER Axel. \emph{DZone} [online]. June 28, 2011, [cit. 2015-07-08]. Available from: https://dzone.com/articles/brief-history-ecmascript

\bibitem{svg}
Scalable Vector Graphics (SVG) 1.1 (Second Edition). \emph{The World Wide Web Consortium (W3C)} [online]. 16 August 2011, [cit. 2915-07-08]. Available from: http://www.w3.org/TR/SVG/

\bibitem{blink_no_smil}
Web Platform Features: Deprecate SMIL. \emph{Chromium Dashboard} [online]. [cit. 2015-07-16]. Available from: https://www.chromestatus.com/features/5371475380928512

\bibitem{web_animation_api}
Web Animations 1.0. \emph{The World Wide Web Consortium (W3C)} [online]. 5 June 2014, [cit. 2015-07-16]. Available from: http://www.w3.org/TR/web-animations/

\bibitem{web_animations_draft}
Web Animations. \emph{The World Wide Web Consortium (W3C)} [online]. 16 July 2015, [cit. 2015-07-16]. Available from: http://w3c.github.io/web-animations/

\bibitem{ms_no_anim}
Web Animations JavaScript API. \emph{status.modern.IE} [online]. [cit. 2015-07-16]. Available from: https://status.modern.ie/webanimationsjavascriptapi

\bibitem{anim_api_partial}
Web Animations API. \emph{Can I use?} [online]. [cit. 2015-07-16]. Available from: http://caniuse.com/\#feat=web-animation

\bibitem{mdn_audio_formats}
Media formats supported by the HTML audio and video elements. \emph{Mozilla Developer Network (MDN)} [online]. Last updated on June 9, 2015, [cit. 2015-07-16]. Available from: https://developer.mozilla.org/en-US/docs/Web/HTML/Supported\_media\_formats

\bibitem{dom}
Document Object Model. \emph{Wikipedia, the free encyclopedia} [online]. Last modified on 12 June 2015, [cit. 2015-07-08]. Available from: https://en.wikipedia.org/wiki/Document\_Object\_Model

\bibitem{dom_mouse_events}
Document Object Model (DOM) Level 2 Events Specification. PIXLEY Tom. \emph{The World Wide Web Consortium (W3C)} [online]. 13 November, 2000, [cit. 2015-07-08]. Available from: http://www.w3.org/TR/DOM-Level-2-Events/

%%
%% 06 file format
%%

\bibitem{svg_extending}
Scalable Vector Graphics (SVG) 1.1 (Second Edition). \emph{The World Wide Web Consortium (W3C)} [online]. 16 August 2011, [cit. 2915-07-08]. Available from: http://www.w3.org/TR/SVG/extend.html


%%
%% 07 implementation
%%

\bibitem{mdn_prototype_chain}
Inheritance and the prototype chain. \emph{Mozilla Developer Network (MDN)} [online]. Last updated on April 2, 2015, [cit. 2015-07-08]. Available from: https://developer.mozilla.org/en-US/docs/Web/JavaScript/Inheritance\_and\_the\_prototype\_chain

\bibitem{mdn_memory_management}
Memory Management. \emph{Mozilla Developer Network (MDN)} [online]. Last updated on 11. 4. 2015, [cit. 2015-07-08]. Available from: https://developer.mozilla.org/cs/docs/Web/JavaScript/Memory\_Management

\bibitem{typescript}
\emph{TypeScript} [online]. © 2012-2015, [cit. 2015-07-08]. Available from: http://www.typescriptlang.org/


\bibitem{loose_coupling}
Coupling (computer programming). \emph{Wikipedia, the free encyclopedia} [online].  Last modified on 13 July 2015, [cit. 2015-07-14]. Available from: http://en.wikipedia.org/wiki/Coupling\_(computer\_programming)

\bibitem{html5}
HTML Living Standard. \emph{The Web Hypertext Application Technology Working Group (WHATWG)} [online]. Last updated on 5 May 2015, [cit. 2015-07-08]. Available from: https://html.spec.whatwg.org/\#is-this-html5

\bibitem{html5_canvas}
HTML5. \emph{The World Wide Web Consortium (W3C)} [online]. 24 June 2010, [cit. 2015-07-08]. Available from: http://www.w3.org/TR/2010/WD-html5-20100624/the-canvas-element.html

\bibitem{xhr}
XMLHttpRequest Living Standard. \emph{The Web Hypertext Application Technology Working Group (WHATWG)} [online]. Last updated 14 July 2015, [cit. 2015-07-08]. Available from: https://xhr.spec.whatwg.org/\#document-response


\bibitem{dynadraw}
Dynadraw: A dynamic drawing technique. HAEBERLI Paul. \emph{GRAFICAObscura} [online]. June 1989, [cit. 2015-07-08]. Available from: http://www.graficaobscura.com/dyna/

\bibitem{inkscape_dynadraw}
Inkscape [online]. [cit. 2015-07-16]. Available from: http://bazaar.launchpad.net/~inkscape.dev/inkscape/trunk/view/head:/src/ui/tools/calligraphic-tool.h

\bibitem{eva_sharp}
EVA animater plaza. \emph{SHARP} [online]. [cit. 2015-07-08]. Available from: http://www.sharp.co.jp/sc/excite/evademo/evahome.htm

\bibitem{eva_wikipedia}
Extended Vector Animation. \emph{Wikipedia, the free encyclopedia} [online]. Last modified on 13 December 2012, [cit. 2015-07-08]. Available from: https://en.wikipedia.org/wiki/Extended\_Vector\_Animation

\bibitem{swf_wiki}
SWF. \emph{Wikipedia, the free encyclopedia} [online]. Last modified on 11 May 2015, [cit. 2015-07-08]. Available from: https://en.wikipedia.org/wiki/SWF

\bibitem{wav}
WAVE PCM soundfile format. SAPP Craig Stuart [online]. [cit. 2015-07-09]. Available from: http://soundfile.sapp.org/doc/WaveFormat/

%%
%% 07 implementation
%%

\bibitem{ecmascript}
ECMAScript Programming Language. \emph{ecmascript} [online]. [cit. 2015-07-15]. Available from: http://www.ecmascript.org/

\bibitem{get_user_media}
Media Capture and Streams. \emph{The World Wide Web Consortium (W3C)} [online]. 14 April 2015, [cit. 2015-07-09]. Available from: http://www.w3.org/TR/mediacapture-streams/\#dom-mediadevices-getusermedia

\bibitem{mic}
Web Audio API. \emph{The World Wide Web Consortium (W3C)} [online]. 10 October 2013, [cit. 2015-07-09]. Available from: http://www.w3.org/TR/webaudio/\#ScriptProcessorNode-section

\bibitem{mic_deprecated}
Web Audio API. \emph{The World Wide Web Consortium (W3C)} [online]. 21 June 2015, [cit. 2015-07-09]. Available from: https://webaudio.github.io/web-audio-api/\#the-scriptprocessornode-interface---deprecated

\bibitem{audio_worker}
Web Audio API. \emph{The World Wide Web Consortium (W3C)} [online]. 21 June 2015, [cit. 2015-07-09]. Available from: http://webaudio.github.io/web-audio-api/\#the-audioworkernodeprocessor-interface	

\bibitem{mic_pcm}
Web Audio API. \emph{The World Wide Web Consortium (W3C)} [online]. 10 October 2013, [cit. 2015-07-09]. Available from: http://www.w3.org/TR/webaudio/\#AudioBuffer

\bibitem{wiki_pcm}
Pulse-code modulation. \emph{Wikipedia, the free encyclopedia} [online]. Last modified on 5 July 2015, [cit. 2015-07-09]. Available from: https://en.wikipedia.org/wiki/Pulse-code\_modulation

\bibitem{websocket}
The WebSocket Protocol [online]. December 2011, [cit. 2015-07-09]. Available from: https://tools.ietf.org/html/rfc6455

%\bibitem{websockets_api}
%The WebSocket API, W3C Candidate Recommendation 20 September 2012, viewed July 9, 2015 [online]
%http://www-mmsp.ece.mcgill.ca/documents/AudioFormats/WAVE/WAVE.html

\bibitem{bezier}
An introduction to splines for use in computer graphics and geometric modeling, Bartels, Richard H, p. 160
(https://cs.uwaterloo.ca/research/tr/1983/CS-83-09.pdf)

\bibitem{catmull_rom}
{\sc Donald} House: Spline Curves [online], [cit. 2015-07-15], Available from: http://people.cs.clemson.edu/~dhouse/courses/405/notes/splines.pdf

\bibitem{catmull_bezier}
{\sc Millington} Ian: Matrices and Conversions for Uniform Parametric Curves [online], \emph{The R'n'D Guy}, [cit. 2015-07-15] Available from: http://therndguy.com/papers/curves.pdf

\bibitem{wacom_discontinued}
{\sc Schuh} Justin: The Final Countdown for NPAPI [online], Chromium Blog, [cit. 2015-07-16] Available from: http://blog.chromium.org/2014/11/the-final-countdown-for-npapi.html

\bibitem{gang_of_four}
{\sc Gamma} Erich, {\sc Johnson} Ralph, {\sc Helm} Richard, {\sc Vlissides} John
\emph{Design Patterns: Elements of Reusable Object-Oriented Software}
1 edition
Addison Wesley, 1994
ISBN: 978-0201633610



%%
%% Integration
%%

\bibitem{html_viewport}
https://developers.google.com/speed/docs/insights/ConfigureViewport

\end{thebibliography}
